% --- Project Euler Problem 55 --- %
\begin{tcbProblem}[label={problem:0055:question:Eng}]
	If we take \( 47 \), reverse and add, \( 47 \mathplus 74 \equal 121 \), which is palindromic.

	Not all numbers produce palindromes so quickly. For example,
	\begin{align*}
		\relax &  349 \mathplus  943 \equal 1292 \\%
		\relax & 1292 \mathplus 2921 \equal 4213 \\%
		\relax & 4213 \mathplus 3124 \equal 7337 %
	\end{align*}

	That is, \( 349 \) took three iterations to arrive at a palindrome.

	Although no one has proved it yet, it is thought that some numbers, like \( 196 \), never produce a palindrome.
	A number that never forms a palindrome through the reverse and add process is called a Lychrel number.
	Due to the theoretical nature of these numbers, and for the purpose of this problem, we shall assume that a number is Lychrel until proven otherwise.
	In addition you are given that for every number below ten-thousand, it will either
	\begin{enumerate*}[label={(\roman*)}]
		\item become a palindrome in less than fifty iterations, or,
		\item no one, with all the computing power that exists, has managed so far to map it to a palindrome.
	\end{enumerate*}
	In fact, \( 10677 \) is the first number to be shown to require over fifty iterations before producing a palindrome: \( 4668731596684224866951378664 \) (53 iterations, 28-digits).

	Surprisingly, there are palindromic numbers that are themselves Lychrel numbers; the first example is \( 4994 \).

	How many Lychrel numbers are there below ten-thousand?

	\emph{NOTE}: Wording was modified slightly on 24 April 2007 to emphasise the theoretical nature of Lychrel numbers.
	\par%
	\hrefOriginalPage{55}%
\end{tcbProblem}
